Liberal Might Win 31.80% of Popular Votes with 100% Turnout Rate

### 2020-12-30 Outputs/Paper/paper.Rmd
try to knit again
try to knit again. succeed!

---
title: "Liberal Might Win 31.80% of Popular Votes with 100% Turnout Rate"
author: "Yijie Zhao"
date: "22 December 2020"
output: html_document
bibliography: references.bib
---

@@

# calculate overall vote share for Liberal
sum(vote_Liberal_est$proportion1)
```

>>>>

---
title: "Liberal Might Win 31.80% of Popular Votes with 100% Turnout Rate"
author: "Yijie Zhao"
date: "22 December 2020"
output:
  pdf_document: default
  html_document: default
bibliography: references.bib
---

@@

# calculate overall vote share for Liberal
sum(vote_Liberal_census$proportion1)
```
